Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-30 Ben_Manuscripts/Paper1/Outline.tex
minor updates

  Experimental WAXS measurements encode all structural details. 
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-pi.
	\item A weak intensity line is located at exactly half the qz value of
	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Equilibrated systems built according to the 3.7 \angstrom 
	layer spacing implied by R-pi are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
	\item We will refer to this system as Basin A (Figure~\ref{fig:280K_pore}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called Basin B (Figure~\ref{fig:340K_pore}).
	\item It is apparent that this LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Understanding which phase exists experimentally is necessary in order
	to appropriately study the system.
  \end{itemize}

@@

  The model gives reasonable estimates of ionic conductivity for both phases.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Table~\ref{table:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty.
	\item  This is especially true of the value calculated for Basin B using
	the collective diffusion model. % TODO: Run Basin B out longer
	\item Basin A collective diffusion calculations were generated from a 
	500 ns simulation.
	\item In both cases, our calculated values would benefit from longer simulations. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
	\item Conductivity is enhanced in Basin B due to a higher sodium ion diffusivity.
	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
	Sodium ions have less ites to move to in Basin A.
	\item No experimental evidence of this trend. May Xunda will find something
	\item In both cases, our calculated values for Basin A are higher than the 
	experimental values, as expected. 
	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
	\item However, the real system, although mostly aligned and straight, has a 
	distribution of azimuthal angles, meaning that the pores have a degree of 
	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
	fold increase in ionic conductivity. We would expect additional gains in a 
	perfectly aligned system.
  \end{itemize}

@@

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  Basin A.
  \begin{itemize}  %BJC: working on the following
  	\item Distribution of crosslinks
	\item Pore spacing
	\item X-ray diffraction
	\item Ionic Conductivity
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}

>>>>

  Experimental WAXS measurements encode all remaining structural details. 
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-pi.
	\item A weak intensity line is located at exactly half the qz value of
	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Equilibrated systems built according to the 3.7 \angstrom 
	layer spacing implied by R-pi are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
	\item We will refer to this system as Basin A (Figure~\ref{fig:abasin}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
	\item It is apparent that this LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Understanding which phase exists experimentally is necessary in order
	to appropriately study the system.
  \end{itemize}

  \begin{figure}
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:abasin}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close.png}
                \caption{}\label{fig:bbasin}
        \end{subfigure}
	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
	hollow cylindrical pore while pores in Basin B (b) are characterized by a
	higher degree of radial disorder}\label{fig:basins}
  \end{figure}

@@

  The model gives reasonable estimates of ionic conductivity when compared to 
  experiment.
  \begin{itemize}
  	\item Calculated values of ionic conductivity obtained using the Nernst 
	Einstein relation and Collective Diffusion model are compared in 
	Table~\ref{table:conductivity}.
	\item The two methods agree with each other within error, although the 
	uncertainty obtained using the Collective Diffusion model is much higher.
	\item Much longer simulations are needed to lower the uncertainty. % TODO: Run Basin B out longer at same conditions as A
	\item Collective diffusion calculations were generated from 
	500 ns simulations.
	\item Our calculated values would benefit from longer simulations. 
	\item For this reason we will likely only use the Nernst Einstein relation
	in future calculations of this type. 
	\item Interestingly, Basin B has a higher ionic conductivity than Basin A.
	\item We hypothesize that conductivity is enhanced in Basin B due to a 
	higher sodium ion diffusivity.
	\item Transport of sodium is likely facilitated by the homogeneity of Basin B.
	Sodium ions have less sites to move to in Basin A.
	\item There is currently no experimental evidence of this trend. Maybe Xund will find something
	\item In both cases, our calculated values for Basin A are higher than the 
	experimental values, as expected. 
	\item Some of the discrepancy is likely a result of using an imperfect forcefield. 
	\item However, the real system, although mostly aligned and straight, has a 
	distribution of azimuthal angles, meaning that the pores have a degree of 
	tortuosity which lowers the effective ionic conductivity of the bulk membrane. 
	\item The ordering from isotropic to mostly aligned mesophases showed an 85 
	fold increase in ionic conductivity. We would expect additional gains in a 
	perfectly aligned system.
  \end{itemize}

@@

  We applied the crosslinking algorithm to the equilibrated sandwiched structure in 
  Basin A.
  \begin{itemize}  %BJC: working on the following. The following is what I expect
  	\item There is an even distribution of crosslinks between same monomer tails, 
	between monomers in the same pore and between monomers in different pores 
	including periodic boundaries.
	\item The distance between pores shrinks by 1 \angstrom after the system is 
	crosslinked
	\item Major features are still present in the X-ray diffraction
	\item The ionic conductivity is higher/lower in the crosslinked system
  \end{itemize}
  %BJC: THe following figure will be replaced with one representative of the new
  % data I am  collecting above.
  \begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
  \end{figure}
